Notes on Perturbational Quantities

### 2008-08-14 docs/pert_notes/paper.tex
correct the final enthalpy update part

\subsection{Predicting $\rho'$ (predict\_rho = F - default)}

@@

make\_edge\_scal in scalar\_advance and the underbraced term in (\ref{rhoprime equation}) 

@@

\item We call make\_edge\_state\_1d using the underbraced term in 

@@

This term is used to advect $\rho_0$ in advect\_base and therefore must also be used 
to compute $\eta_\rho$, which will be used in correct\_base.

@@

compute $\rho_0^{(2)}$ from $\rho_0^n$ using advect\_base, which advances equation 

@@

that we have not called correct\_base yet, which computes  $\rho_0^{n+1}$ from $\rho_0^{(2)}$. 

@@

accounted for in react\_state, and the associated discretization is

@@

\subsection{Predicting $(\rho h)'$ (enthalpy\_pred\_type = 1 - default)}
Due to operator splitting, the call to react\_state has already been made.  Hence, the goal 

@@

already accounted for in react\_state

@@

through the complete evolution of $(\rho h)_0$ using $(\rho h)_0^n \rightarrow$ react\_base 
$\rightarrow (\rho h)_0^{(1)} \rightarrow$ advect\_base 
$\rightarrow (\rho h)_0^{(2)} \rightarrow$ react\_base $\rightarrow (\rho h)_0^{n+1}$.  
There is no correct\_base function for $(\rho h)_0$ written yet, nor is any adjustment made 

@@

edges using make\_edge\_scal in scalar\_advance and the underbraced term in 

@@

- \nabla\cdot\left[(\rho h)_0^{n+\half,{\rm pred}}w_0\eb_r\right].

@@

+ (\rho h)'\right]\left(\Ubt + w_0\eb_r\right)\right\}.

>>>>

\subsection{Predicting $\rho'$ ({\tt predict\_rho = F} - default)}

@@

{\tt make\_edge\_scal} in {\tt scalar\_advance} and the underbraced term in (\ref{rhoprime equation}) 

@@

\item We call {\tt make\_edge\_state\_1d} using the underbraced term in 

@@

This term is used to advect $\rho_0$ in {\tt advect\_base} and therefore must also be used 
to compute $\eta_\rho$, which will be used in {\tt correct\_base}.

@@

compute $\rho_0^{(2)}$ from $\rho_0^n$ using {\tt advect\_base}, which advances equation 

@@

that we have not called {\tt correct\_base} yet, which computes  $\rho_0^{n+1}$ from $\rho_0^{(2)}$. 

@@

accounted for in {\tt react\_state}, and the associated discretization is

@@

\subsection{Predicting $(\rho h)'$ ({\tt enthalpy\_pred\_type = 1} - default)}
Due to operator splitting, the call to {\tt react\_state} has already been made.  Hence, the goal 

@@

already accounted for in {\tt react\_state}

@@

through the complete evolution of $(\rho h)_0$ using $(\rho h)_0^n \rightarrow$ {\tt react\_base}
$\rightarrow (\rho h)_0^{(1)} \rightarrow$ {\tt advect\_base}
$\rightarrow (\rho h)_0^{(2)} \rightarrow$ {\tt react\_base} $\rightarrow (\rho h)_0^{n+1}$.  
There is no {\tt correct\_base} function for $(\rho h)_0$ written yet, nor is any adjustment made 

@@

edges using {\tt make\_edge\_scal} in {\tt scalar\_advance} and the underbraced term in 

@@

\underbrace{- \nabla\cdot\left[(\rho h)_0^{n+\half,{\rm pred}}w_0\eb_r\right] + \psi}_{\text{this term used to come in through} ~ (\rho h)_0^{n+1} - (\rho h)_0^n} + \wt\frac{\partial p_0}{\partial r} \enskip .

@@

+ (\rho h)'\right]\left(\Ubt + w_0\eb_r\right)\right\} + \wt\frac{\partial p_0}{\partial r} + \psi  \enskip .
